Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-08-12 Report/ieee_journal.tex
Updated KKT MSE and figures
stfloats
updated tex
update

\documentclass[11pt,draftcls,onecolumn]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym}
\usepackage[ruled]{algorithm2e}
\usepackage{caption,subcaption}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}

@@

\subsection{Decomposition by solving \ac{KKT} equations} \label{sec-4.3}

@@

\section{Simulation Results} \label{sec-5}
\subsection{Centralized Solutions}
\input{simulation_results}

>>>>

\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym}
\usepackage[ruled]{algorithm2e}
\usepackage{subfig,subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}

@@

\subsection{Decomposition using \ac{KKT} equations in \ac{MSE} formulation} \label{sec-4.3}

@@

\section{Simulation Results} \label{sec-5}
\input{simulation_intro}

\subsection{Centralized Solutions}
\input{simulation_results}

### 2014-08-12 Report/wsrm_formulation.tex
update

Now, the optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}}, which is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{w}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
\end{IEEEeqnarray}
When the number of queued packets for each user is significantly large, the queue minimizing objective is in fact the sum rate maximization problem. Since the optimal receivers for the sum rate maximization problem with the fixed transmit precoders is the \ac{MMSE} receivers, we can use the \ac{MMSE} receiver as the receive beamformers without affecting the optimal solution. When the number of queued packets are smaller than the achievable transmission rate of the users, the receiver defined by \eqref{eqn-9--1} provides better solution compared to the \ac{MMSE} based receivers given by
\begin{IEEEeqnarray}{rCl}\label{eqn-10}
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber \\
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber
\end{IEEEeqnarray}
For the single receive antenna scenario, the receivers in \eqref{eqn-9--1} and \eqref{eqn-10} achieves the same optimal point, since the \ac{SINR} expression is independent of the receive beamformer.

>>>>

Now, the optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}}, which is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{w}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
\end{IEEEeqnarray}
Now, solving for the optimal receiver using \ac{KKT} conditions, we obtian the following expression in an iterative manner around the \ac{SCA} point \me{\mbf{\tilde{w}}_{l,k,n}}
\begin{subeqnarray} \label{opt-rx}
\mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
\mvec{w}{l,k,n} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \tilde{\mbf{w}}_{l,k,n} }{\|\tilde{\mbf{w}}_{l,k,n} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{R}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
\end{subeqnarray}
where the fractional term inside the brace is a constant. It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-10}
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber \\
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber
\end{IEEEeqnarray}
